### 2018-10-08 Sections/essay_security_implications_of_the_global_quantum_internet.tex
Some quotes

@@

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves.
\if 1\pubmode
\else
Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}.

>>>>

\famousquote{Truth is treason in the empire of lies.}{George Orwell}
\newline

@@

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves.
\if 1\pubmode
\else
Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{``I don't even know why any of us are here. This is the worst job I've ever had."}.
